Bayesian Statistical Modeling with Predictors from LLMs

### 2024-06-13 04-paper/paper-LLM-probmod.tex
added pic and acknowledgements

The paper is structured as follows.
Section~\ref{experiment-reference-games} describes an experiment with human participants with a text-based reference game.
Section~\ref{sec:model-pred-from} introduces the Rational Speech Act (RSA) model for the human data from the reference game experiment.
Section~\ref{sec:item-level-pred} exposes a statistical model for item-level predictions derived from LLM scores and investigates whether this adequately captures the human data at the item-level based on scores from GPT-3.5 \citep{BrownMann2020:Language-Models}.
Section~\ref{llm-predictions-for-reference-games} discusses different ways of deriving probabilistic predictions from LLMs at the condition-level and compares them against the human data and each other.
Finally, Section~\ref{sec:gener-other-llm} explores whether previous results generalize to other LLM backends by investigating different versions of LLaMA2 \citep{TouvronLavril2023:LLaMA:-Open-and}.

@@

>>>>

The paper is structured as follows.
Section~\ref{experiment-reference-games} describes an experiment with human participants with a text-based reference game.
Section~\ref{sec:model-pred-from} introduces the Rational Speech Act (RSA) model for the human data from the reference game experiment.
Section~\ref{sec:item-level-pred} exposes a statistical model for item-level predictions derived from LLM scores and investigates whether this adequately captures the human data at the item-level based on scores from GPT-3.5 \citep{BrownMann2020:Language-Models}.
Section~\ref{llm-predictions-for-reference-games} discusses different ways of deriving probabilistic predictions from LLMs at the condition-level and compares them against the human data and each other.
Finally, Section~\ref{sec:gener-other-llm} explores whether previous results generalize to other LLM backends by investigating different versions of LLaMA2 \citep{TouvronLavril2023:LLaMA:-Open-and}.\footnote{
  All data and code is available at \url{https://osf.io/f6j3a/?view_only=5e820cc8bbee4549aed58dc252ba61b9}.
}

@@

\section*{Acknowledgements}
Thanks to Robert D. Hawkins and Thomas Brochhagen for insightful comments.
We gratefully acknowledge support by the state of Baden-Württemberg, Germany, through the computing resources provided by bwHPC and the German Research Foundation (DFG) through grant INST 35/1597-1 FUGG.
MF is a member of the Machine Learning Cluster of Excellence, EXC number 2064/1 – Project number 39072764.
